### 2017-12-15 derivations.tex
update temperature

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage[
    backend=biber,
    style=numeric,
    citestyle=numeric
]{biblatex}
\addbibresource{derivations.bib}
\usepackage[breaklinks=true, linkcolor=blue, citecolor=blue, colorlinks=true]{hyperref}
% multiple eq references
\usepackage{cleverref}

\newcommand{\pluseq}{\mathrel{{+}{=}}}
\newcommand{\minuseq}{\mathrel{{-}{=}}}
\newcommand{\ns}{\ensuremath{{N_{sp}}}}
\newcommand{\conp}{constant-pressure}
\newcommand{\conv}{constant-volume}
\newcommand{\dconp}{\ensuremath{,\qquad\text{for \conp}}}
\newcommand{\dconv}{\ensuremath{,\qquad\text{for \conv}}}
\newcommand{\Ru}{\ensuremath{\mathcal{R}}}

\begin{document}
\section{Introduction}
This document contains the complete derivations for \texttt{pyJac} v2.0, which generates code to evaluate the chemical source term and analytical chemical kinetic Jacobians of \conp\slash\conv, fixed-mass, adiabatic reactors.

@@

Combining~\cref{source:param_incomplete,source:total_molar,source:spec} gives the final form of the pressure and volume terms:
\begin{subequations}
\label{source:param_complete}
\begin{align}
\frac{\text{d} V }{\text{d} t } &= V \left(\frac{T R_u}{P} \sum_{k=1}^{-1 + \ns} \left(1 - \frac{W_{k}}{W_{\ns}}\right) \dot{\omega}_{k} + \frac{1}{T} \frac{\text{d} T }{\text{d} t }\right)\dconp, \\
\frac{\text{d} P }{\text{d} t } &= \frac{P}{T} \frac{\text{d} T }{\text{d} t } + T R_u \sum_{k=1}^{-1 + \ns} \left(1 - \frac{W_{k}}{W_{\ns}}\right) \dot{\omega}_{k}\dconv
\end{align}
\end{subequations}

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb}
\usepackage[
    backend=biber,
    style=numeric,
    citestyle=numeric
]{biblatex}
\addbibresource{derivations.bib}
\usepackage[breaklinks=true, linkcolor=blue, citecolor=blue, colorlinks=true]{hyperref}

\newcommand{\pluseq}{\mathrel{{+}{=}}}
\newcommand{\minuseq}{\mathrel{{-}{=}}}
\newcommand{\ns}{\ensuremath{{N_{sp}}}}
\newcommand{\conp}{CONP}
\newcommand{\conv}{CONV}
\newcommand{\dconp}{\ensuremath{,\qquad\text{for \conp}}}
\newcommand{\dconv}{\ensuremath{,\qquad\text{for \conv}}}
\newcommand{\Ru}{\ensuremath{\mathcal{R}}}

\begin{document}
\section{Introduction}
This document contains the complete derivations for \texttt{pyJac} v2.0, which generates code to evaluate the chemical source term and analytical chemical kinetic Jacobians of \conp\slash\conv, fixed-mass, adiabatic reactors.
Note that equations specific to the constant-pressure or constant-volume derivation will be marked with \conp or \conv respectively

@@

Combining~\eqref{source:spec},\eqref{source:param_incomplete},\eqref{source:total_molar} gives the final form of the pressure and volume terms:
\begin{subequations}
\label{source:param_complete}
\begin{align}
\frac{\text{d} V }{\text{d} t } &= V \left(\frac{T R_u}{P} \sum_{k=1}^{-1 + \ns} \left(1 - \frac{W_{k}}{W_{\ns}}\right) \dot{\omega}_{k} + \frac{1}{T} \frac{\text{d} T }{\text{d} t }\right)&\dconp, \\
\frac{\text{d} P }{\text{d} t } &= \frac{P}{T} \frac{\text{d} T }{\text{d} t } + T R_u \sum_{k=1}^{-1 + \ns} \left(1 - \frac{W_{k}}{W_{\ns}}\right) \dot{\omega}_{k}&\dconv
\end{align}
\end{subequations}
Additionally, the temperature source terms may be expanded to remove references to the last species' source term and overall production rate:
\begin{subequations}
\label{source:temperature_complete}
\begin{align}
\frac{\text{d} T }{\text{d} t } = - \frac{\sum_{k=1}^{-1 + \ns} \left(H_{k} - \frac{W_{k} H_{\ns}}{W_{\ns}}\right) \dot{\omega}_{k}}{[C] {C_{p,\ns}} + \sum_{k=1}^{-1 + \ns} \left(- {C_{p,\ns}} + {C_{p, k}}\right) [C]_{k}}\dconp,\\
\frac{\text{d} T }{\text{d} t } = - \frac{\sum_{k=1}^{-1 + \ns} \left(U_{k} - \frac{W_{k} U_{\ns}}{W_{\ns}}\right) \dot{\omega}_{k}}{[C] {C_{v,\ns}} + \sum_{k=1}^{-1 + \ns} \left(- {C_{v,\ns}} + {C_{v, k}}\right) [C]_{k}}\dconv
\end{align}
\end{subequations}
